Self Referencing Sequences

### 2014-10-27 draft.tex
gave explanation for why sequence of 1,2,3 starting at 2 and starting at 3 are the same. edited up to conjecture 1

In this section, we consider a slightly weaker definition of equivalence. Consider, for example, sequences generated by $\{1,2,3\}$. Theorem~\ref{independentsequences} shows that the sequence starting with 2
\begin{align*}
2,2,3,3,1,1,1,2,2,2,3,1,2,3,3,1,1,2,2,3,3,3,\dots
\end{align*}
and the sequence starting with 3
\begin{align*}
3,3,3,1,1,1,2,2,2,3,1,2,3,3,1,1,2,2,3,3,3,\dots
\end{align*}
are independent in the sense that neither sequence is exactly contained in the other. However, if we delete the first two numbers of the sequence starting with 2, and the first number of the sequence starting with 3, we get 
\begin{align*}
3,3,1,1,1,2,2,2,3,1,2,3,3,1,1,2,2,3,3,3,\dots
\end{align*}
in both cases. (Need to further justify why these two are the same, probably with a reading distance argument)

@@

We now introduce a notion which will help us categorize sequences as equivalent. 
\begin{definition} Consider a sequence $x$. We say define the read distance for an element $x_i$ as the number of terms in between it and the beginning of the $i$th block of numbers. We denote this as $Rd(x_i)$. 
\end{definition}
The read distance can be any nonnegative integer. For example if we consider the sequence $a_i$ generated by $\{1,2,3\}$ beginning with a 2  
\begin{align*}
2,2,3,3,1,1,1,2,2,2,3,1,2,3,3,1,1,2,2,3,3,3,\dots
\end{align*}
the read distance for the $a_1$ (the first two) is $0$ as the first block of numbers starts at the first number, the read distance for $a_2$ (the second two) is $1$ as the second block of numbers starts at the third number. We can continue to calculate the read distances for this sequence and see that they form a monotonically increasing sequence $0,1,2,4,6,6,6,6,7,8,9,\ldots$. From this we might suspect that the read distance for any self referencing sequence will also be monotonically increasing. We can in fact show a much stronger result. 
\begin{lemma} 
\label{readdistformula}
Let $a_i$ be any self referencing sequence generated by some set of positive integers. Then the read distance for the element $a_i$ for $i>1$ is 
\begin{equation*}
\sum_{k=1}^{i-1}( a_k - 1)
\end{equation*} 
\end{lemma}
\begin{proof}
We will prove this using induction. We know that for $i=1$ the read distance is $0$, as the first block always starts at the first number. For the base case $i=2$ we must show that the read distance is $a_1-1$. Well we know that the first block will be of length $a_1$ since the sequence is self referencing, therefore the second block will begin at \emph{position} $a_1$. The number of elements between position $a_1$ and $2$ is exactly $a_1 -1$.

>>>>

In this section, we consider a slightly weaker definition of equivalence. Consider, for example, sequences generated by $C = \{1,2,3\}$. Theorem~\ref{independentsequences} shows that the sequence starting with 2
\begin{align*}
2,2,3,3,1,1,1,2,2,2,3,1,2,3,3,1,1,2,2,3,3,3,\dots
\end{align*}
and the sequence starting with 3
\begin{align*}
3,3,3,1,1,1,2,2,2,3,1,2,3,3,1,1,2,2,3,3,3,\dots
\end{align*}
are independent in the sense that neither sequence is exactly contained in the other. However, if we delete the first two numbers of the sequence starting with 2, and the first number of the sequence starting with 3, we get 
\begin{align*}
3,3,1,1,1,2,2,2,3,1,2,3,3,1,1,2,2,3,3,3,\dots
\end{align*}
in both cases. Lets look at the state of the algorithm that generates both sequences. After the first block, the execution of the algorithm of $s(C, 2)$ right after placing the $3$'s (in the 4th and 5th position), the algorithm is in state corresponding to:
\begin{itemize}
\item block size $3$
\item no elements on the current block
\item starting number is $1$
\end{itemize}.   
If we look at the execution of the algorithm that generates $s(C, 3)$ after placing the first three $3$'s, the algorithm is in state corresponding to:
\begin{itemize}
\item block size $3$
\item no elements on the current block
\item starting number is $1$
\end{itemize}
Therefore, since the states are the same, the same sequence will be generated after the 4th position of $s(C, 2)$ and after the $3rd$ position of $s(C, 3)$ will be the same. By inspection, we can see we can include $2$ of the 3's.

@@

We now introduce a notion which will help us categorize sequences as equivalent. 
\begin{definition} Consider a sequence $x$. We define the read distance for an element $x_i$ as the number of terms in between it and the beginning of the $i$th block of numbers. We denote this as $Rd(x_i)$. 
\end{definition}
The read distance can be any nonnegative integer. For example if we consider the sequence $a_i$ generated by $\{1,2,3\}$ beginning with a 2  
\begin{align*}
2,2,3,3,1,1,1,2,2,2,3,1,2,3,3,1,1,2,2,3,3,3,\dots
\end{align*}
the read distance for the $a_1$ (the first two) is $0$ as the first block of numbers starts at the first number, the read distance for $a_2$ (the second two) is $1$ as the second block of numbers starts at the third number. We can continue to calculate the read distances for this sequence and see that they form a monotonically increasing sequence $0,1,2,4,6,6,6,6,7,8,9,\ldots$. From this we might suspect that the read distance for any self referencing sequence will also be monotonically increasing. We can in fact show a much stronger result. 
\begin{lemma} 
\label{readdistformula}
Let $a_i$ be any self referencing sequence generated by some set of positive integers. Then the read distance for the element $a_i$ for $i>1$ is 
\begin{equation*}
\sum_{k=1}^{i-1}( a_k - 1)
\end{equation*} 
\end{lemma}
\begin{proof}
We will prove this using induction. We know that for $i=1$ the read distance is $0$, as the first block always starts at the first number. For the base case $i=2$ we must show that the read distance is $a_1-1$. Well we know that the first block will be of length $a_1$ since the sequence is self referencing, therefore the second block will begin at \emph{position} $a_1$. The number of elements between position $a_1$ and $2$ is exactly $a_1 -1$.
